Reproducible Research: Peer Assessment 1
========================================


## Loading and preprocessing the data

```{r}
steps = read.csv(header=T, file="activity.csv")
uniqueDaysList = unique(steps$date)
uniqueIntervalList = unique(steps$interval)
```

## What is mean total number of steps taken per day?

Histogram on amount of steps daily:
```{r}
sumPerDay = lapply(uniqueDaysList, function(x) { sum(na.rm = T, steps[ steps$date == x, "steps" ] ) } )
hist(as.integer(sumPerDay))
```

Mean of steps daily:
```{r}
mean(as.integer(sumPerDay), na.rm = T)
```
Meadian of steps daily:
```{r}
median(as.integer(sumPerDay), na.rm = T)
```

## What is the average daily activity pattern?

Amount of steps in average in different intervals:
```{r}
avgPerInterval = lapply(uniqueIntervalList, function(x) { mean(na.rm = T, steps[ steps$interval == x, "steps" ] ) } )
avgPerIntervalDF = data.frame("interval"=uniqueIntervalList, "avgSteps"=as.double(avgPerInterval))
plot( x=uniqueIntervalList, y=avgPerInterval, type="l")
```
Interval with maximum average steps:
```{r}
avgPerIntervalDF[which.max(avgPerIntervalDF$avgSteps),"interval"]
```

## Imputing missing values

Amount of missign values:
```{r}
amountOfNAs = length( steps[ is.na(steps$steps) | is.na(steps$date) | is.na(steps$interval), 1])
```
Filling empty values with interval average:
```{r}
stepsWithNAsReplaced = mapply(function(x,y) {
    x[is.na(x)] <- avgPerIntervalDF[avgPerIntervalDF$interval == y, "avgSteps"]
    return(x)
    }, steps$steps, steps$interval)
steps = cbind(steps, stepsWithNAsReplaced)
```
Plot histogram on amount of steps daily with NAs as avarage:
```{r}
sumPerDayWithoutNAs = lapply(uniqueDaysList, function(x) { sum(steps[ steps$date == x, "stepsWithNAsReplaced" ] ) } )
hist(as.integer(sumPerDayWithoutNAs))
```

Mean of steps daily with NAs as avarage:
```{r}
mean(as.integer(sumPerDayWithoutNAs))
```
Meadian of steps daily with NAs as avarage:
```{r}
median(as.integer(sumPerDayWithoutNAs))
```

There is bigger impact on mean than the median. Also histogram has altered shape more closely to Gauss curve.


## Are there differences in activity patterns between weekdays and weekends?
```{r}
```
```{r}
```
```{r}
```